High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-20 dev/experimentation.qmd
benchmark set up

@@

```{julia}
# Setup
counterfactual_data = load_multi_class()
M = fit_model(counterfactual_data, :DeepEnsemble)
target = 4
factual = 2
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)

# Search:
generator = GenericGenerator(opt=Descent(0.01))
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
```

```{julia}
niter = 100
nsamples = 100

sampler = CCE.EnergySampler(ce;niter=niter, nsamples=100)
Xgen = rand(sampler, nsamples)
plt = plot(M, counterfactual_data, target=ce.target, xlims=(-5,5),ylims=(-5,5),cbar=false)
scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
```

```{julia}
p1 = plot(ce)
```

```{julia}
using CCE: distance_from_energy
@objective(generator, _ + 0.1distance_l2 + 10.0distance_from_energy)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p2 = plot(ce)
```

```{julia}
using CCE: distance_from_targets
@objective(
    generator, 
    _ + 0.1distance_l2 + 1.0distance_from_energy + 10.0distance_from_targets
)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p3 = plot(ce)
```

>>>>

### Benchmark

```{julia}
#| output: false

# Data:
datasets = Dict(
    :linearly_separable => load_linearly_separable(),
    :overlapping => load_overlapping(),
    :moons => load_moons(),
    :circles => load_circles(),
)

# Models:
models = Dict(
    :MLP => M,
)
```

Then we can simply loop over the datasets and eventually concatenate the results like so:

```{julia}
#| output: false

measure = 
using CounterfactualExplanations.Evaluation: benchmark
bmks = []
for (dataname, dataset) in datasets
    bmk = benchmark(dataset; models=models, generators=generators, suppress_training=true, data_name=dataname)
    push!(bmks, bmk)
end
bmk = reduce(vcat, bmks)
```

@@

```{julia}
counterfactual_data = load_multi_class()
```

```{julia}
#| output: true
#| echo: false
#| label: fig-losses-multi
#| fig-cap: "Illustration of the smooth size loss and the configurable classification loss."

temp = 0.5
p1 = contourf(mach.model, mach.fitresult, X, y; plot_set_loss=true, zoom=0, temp=temp)
p2 = contourf(mach.model, mach.fitresult, X, y; plot_classification_loss=true, target=1, zoom=0, temp=temp, clim=nothing, loss_matrix=ones(4,4))
plot(p1, p2, size=(800,320))
```

```{julia}
#| fig-cap: "Energy-based conditional samples."
#| label: fig-energy-multi

```{julia}
M = CCE.ConformalModel(conf_model, mach.fitresult; likelihood=:classification_multi)
x = select_factual(counterfactual_data,rand(1:size(counterfactual_data.X,2)))
y_factual = predict_label(M, counterfactual_data, x)[1]
target = counterfactual_data.y_levels[counterfactual_data.y_levels .!= y_factual][1]
```

```{julia}
counterfactuals = Dict([name => generate_counterfactual(x, target, counterfactual_data, M, gen; initialization=:identity, converge_when=:generator_conditions, gradient_tol=1e-3) for (name, gen) in generators])
